### 2015-11-28 LaTeX/Revision2/response.tex

	\item The sample includes the 1997 Asian crisis and the 2008 financial crisis. The authors control for the average GDP growth across all countries. The better way to control for time-invariant common shocks is the inclusion of year fixed effects. \\

	\item The authors include binary indicators for whether the country is classified as upper income by the World Bank. It is highly endogeneous to the main variable of interest. \\

	\item Table 2. The authors mention random fixed effects with country, year or country + year. I do not understand what they mean. \\
\end{enumerate}

\begin{itemize}
\item \textcolor{blue}{\emph{
	We adopt the following specification suggested by the reviewer: $\% \delta GDP_{i,t} = \beta_{1}Conflict_{i,t-1} + \beta_{2}Distance_{i,t-1}+\ldots+\zeta_{i,t-1}$, where $Distance_{i,t-1}=0$ when $Conflict_{i,t-1}=0$ and $Distance_{i,t-1}>0$ when $Conflict_{i,t-1}=1$. Additionally, as suggested by the reviewer, we estimate the model with fixed instead of random effects. The results are shown below for both our minimum city distance and minimum capital distance variables, see tables \ref{tab:cityFullPiecewiseFE} and \ref{tab:capFullPiecewiseFE}, respectively. In line with the expectation the reviewer suggested the effect of $\beta_{2}$ is positive across each specification. We have included an appendix item into the paper describing these results and have inserted a footnote within the empirical section referencing this additional analysis.
}} \\

### 2015-11-28 LaTeX/RhodiumAppendix.tex
changes in manuscript

While we contend that random effects are preferred to fixed effects for the reasons outlined in the body of the paper, we have nonetheless repeated our analysis using fixed effects on a full country-year panel dataset. The results are presented in Tables~\ref{tab:cityFullPiecewiseFE} and \ref{tab:capFullPiecewiseFE}. These analyses are performed on the full panel of data and therefore are missing conflict-specific covariates that are unavailable for countries not experiencing civil war. When utilizing this alternative approach we still find strong support for the hypothesis that countries experiencing conflict that is more proximate to capital or major cities are more likely to see significant reductions in GDP growth than conflicts.

@@

>>>>

Here we broaden the random effect conflict-year analysis presented in the paper to a country-year analysis in which we employ a fixed effects framework. Specifically, we estimate the following equation: $\% \delta GDP_{i,t} = \beta_{1}Conflict_{i,t-1} + \beta_{2}Distance_{i,t-1}+\ldots+\zeta_{i,t-1}$, where $Distance_{i,t-1}=0$ when $Conflict_{i,t-1}=0$ and $Distance_{i,t-1}>0$ when $Conflict_{i,t-1}=1$. The $\zeta_{i,t-1}$ term represents our bundle of control variables. This specification provides one way to consider the full sample, control for the presence of armed conflict, and test our key hypothesis regarding the role of conflict proximity to major urban centers. In this specification, we expect the estimate of $\beta_{2}$ to be positive.

The results are presented in Tables~\ref{tab:cityFullPiecewiseFE} and \ref{tab:capFullPiecewiseFE}. In the first column of these tables, we run a pooled country-year analysis in which we include our key variable of interest, distance to conflict, and controls. In the second column, we incorporate country fixed effects and in the last we utilize both country and year fixed effects. When adding year fixed effects we remove our global average GDP growth measure. Since these analyses are performed on the full panel of data we have to exclude the conflict-specific covariates from the PRIO dataset as they are undefined for countries not experiencing civil war.

When utilizing this alternative approach we still find strong support for the hypotheses that countries experiencing conflict more proximate to capital or major cities are more likely to see significant reductions in GDP growth than conflicts that are farther away from these economically vital centers.

@@

When utilizing this alternative dataset we again find significant support for the argument that conflicts more proximate to urban centers have a greater adverse effect on economic growth than those farther away. Additionally, if we switched to a fixed effects framework, such as the one described in the previous appendix section, we still find significant support for the hypotheses laid out in our paper.
